---
title: "Programming Assignment 4"
subtitle: "⚔<br/>with <strong>xaringan</strong>"
author: "Joselyn Rodriguez"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r global-options, include = FALSE}
# settings
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.height = 5,
  echo = FALSE, 
  warning = FALSE,
  fig.retina = 2
)
```

```{r, libraries, comment = '', echo = FALSE, warning = FALSE}
library(tidyverse)
library(ds4ling)
```

```{r load}
data <- read_csv("data_raw/fricatives/fricatives.csv")
head(data)
```

---

# Tidy the data~
```{r tidy}
# I'm sorry this feels like such a hacky way to do this?
data_tidy <- data %>% 
  pivot_longer(., cols = c(s_cog:sh_skewness), names_to = "names", values_to = "value") %>% 
  separate(col = "names", 
                     into =c("phoneme", "measure"),
                     sep = "_") %>% 
  pivot_wider(., names_from = "measure", values_from = "value")
head(data_tidy)
write.csv(data_tidy, "tidy_data.csv")
```

---

# Provide a table of descriptive statistics.
```{r}
d_stats <- summary(data_tidy)
print(d_stats)
```

---

# Make a boxplot of center of gravity as a function of phoneme. 

```{r}
# cog ~ phoneme
data_tidy %>% 
  ggplot() +
    geom_boxplot(aes(x = phoneme, y = cog))
```


---

## In another slide, plot skewness as a function of phoneme. Use a statistical transformation (i.e., not a boxplot).
```{r}
# skewness ~ phoneme 
data_tidy %>% 
  ggplot(aes(x = phoneme, y = skewness)) +
  geom_jitter() +
  stat_summary(fun.data = "mean_cl_boot", colour = "blue")
```
---

# Fit a model that examines center of gravity as a function of skewness for the [s] segments (hint: you will have to transform the data). Make a table of the model summary.

## Transform data first
```{r}
# s_cog ~ s_skewness

# i think you could just do this with the original dataset, but if you wanted to transform again, it'd be:
data_2 <- data_tidy %>% 
              pivot_wider(names_from = "phoneme", values_from = c("cog", "skewness"))
            
model <- lm(cog_s ~ skewness_s, data = data_2)
summary(model)
```

---

# Make a scatter plot that illustrates the relationship in (8).
```{r}
data_2 %>% 
  ggplot(aes(skewness_s, cog_s)) +
    geom_point() +
    geom_smooth(method = "lm")
```
---

# Check model diagnostics (make plots).
```{r}
diagnosis(model)
```
---

# Write up the results (as if it were for a journal article).

Fitting a linear regression model with the equation cog_s ~ skewness_s, we found a significant positive relationship such that as the skewness of /s/ increased, the cog of /s/ also increased ( 



