---
title: "Programming Assignment 4"
author: "Joselyn Rodriguez"
date: "`r Sys.Date()`"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r message=FALSE, include=FALSE}
knitr::opts_chunk$set(
  comment = '',
  fig.width = 6,
  fig.height = 5,
  echo = F, 
  message  = F,
  warning = F,
  fig.retina = 2
)
```

```{r libraries}
library(tidyverse)
library(ds4ling)
```
# 4. First load in the data
```{r load}
data <- read_csv("data_raw/fricatives/fricatives.csv")
head(data, n = 15)
```

---

# 5. Tidy the data~
```{r tidy}
# I'm sorry this feels like such a hacky way to do this?
data_tidy <- data %>% 
  pivot_longer(., cols = c(s_cog:sh_skewness), names_to = "names", values_to = "value") %>% 
  separate(col = "names", 
                     into =c("phoneme", "measure"),
                     sep = "_") %>% 
  pivot_wider(., names_from = "measure", values_from = "value")

head(data_tidy, n = 15)

# write out to csv
write.csv(data_tidy, "data_tidy/tidy_data.csv")
```

---

# 6. Provide a table of descriptive statistics.
```{r}
d_stats <- summary(data_tidy)
print(d_stats)
```

---

# 7.a Make a boxplot of center of gravity as a function of phoneme. 

```{r}
# cog ~ phoneme
data_tidy %>% 
  ggplot() +
    geom_boxplot(aes(x = phoneme, y = cog)) +
    labs(title = "center of gravity of phonemes /s/ and /ʃ/")
```


---

## 7.b In another slide, plot skewness as a function of phoneme. Use a statistical transformation (i.e., not a boxplot).
```{r}
# skewness ~ phoneme 
data_tidy %>% 
  ggplot(aes(x = phoneme, y = skewness)) +
  geom_jitter() +
  stat_summary(fun.data = "mean_cl_boot", colour = "blue") +
  labs(title = "skewness of phonemes /s/ and /ʃ/")
```
---

## 8.a Fit a model that examines center of gravity as a function of skewness for the [s] segments. 

```{r}
# s_cog ~ s_skewness

# Transform data first 

# i think you could just do this with the original dataset, but if you wanted to transform again, it'd be:
data_2 <- data_tidy %>% 
              pivot_wider(names_from = "phoneme", values_from = c("cog", "skewness"))
```


#### 8.b Make a table of the model summary.
```{r}
model <- lm(cog_s ~ skewness_s, data = data_2)
summary(model)
```

---

# 8. Make a scatter plot that illustrates the relationship in (8).
```{r}
data_2 %>% 
  ggplot(aes(skewness_s, cog_s)) +
    geom_point() +
    geom_smooth(method = "lm") +
    labs(title = "center of gravity of /s/ by its skewness")
```
---

# 10. Check model diagnostics (make plots).
```{r, fig.width= 10}
diagnosis(model)
```

Model diagnositics look alright. Not perfectly normal, but it's not too bad. Residuals look fairly homoskedastic. 
---

# 11. Write up the results (as if it were for a journal article).

Fitting a linear regression model of the skewness of /s/ as a predictor of the center of gravity of /s/, we found a significant positive relationship such that as the skewness of /s/ increased, the center of gravity of /s/ also increased (B = 3029.1, SE = 259.1  p < .001). This suggests that there is a positive linear relationship between the skew of /s/ and it's center of gravity. 



